---
title: "simpleRegress"
author: "Alfredo Acevedo"
date: "spring 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 
  
```{r}
ourneck <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(ourneck)
summary.lm(ourneck)
```
The standard error for neck is 5.38. 
  
```{r}
Ourweight <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(Ourweight)
summary.lm(Ourweight)
```  
The standard  error for weight is 5.43.
  
  
  
```{r}
Ourchest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(Ourchest)
summary.lm(Ourchest)
```    
The standard error for chest is 4.94.

  
```{r}
ourheadwth <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(ourheadwth)
summary.lm(ourheadwth)
```  
The standard error is 7.32 for HEADWTH.
  
```{r}
ourheadlen <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(ourheadlen)
summary.lm(ourheadlen)
```    
The standard error for headlen would be 4.24


```{r}
ourage <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(ourage)
summary.lm(ourage)
```  
he standard error for Age would be 7.51.
  
  The order would be from worst to best is age, Headwth, then weight, followed by neck, then chest, and lastly HeadLen  

Age:      RSE: 7.511   ars: 0.5073

Headwth: RSE: 7.32     ars: 0.5321

Weight:  RSE: 5.432,   ars: 0.7423

Neck:    RSE: 5.376    ars: 0.7476

Chest:  RSE: 4.939   ars:0.7869

Headlen: RSE: 4.235    ars:0.8434
  
   